---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `r devtools::as.package(".")$package`

<!-- badges: start -->
[![R-CMD-check](https://github.com/epiforecasts/ForecastHubValidations/workflows/R-CMD-check/badge.svg)](https://github.com/epiforecasts/ForecastHubValidations/actions)
<!-- badges: end -->

This package aims at providing a simple interface to run validations on data
and metadata submitted to a forecast hub. Validation tests can be run at 
different levels (single file, single folder, whole repository) and locally as
well as part of a continuous integration workflow.
For more information, please read the 
["Package design" vignette](https://epiforecasts.github.io/ForecastHubValidations/articles/design.html).

## Installation

You can the latest version of this package from GitHub with:

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("epiforecasts/ForecastHubValidations")
```

## Usage

```{r example}
library(ForecastHubValidations)

validate_repository(
 system.file("testdata", package = "ForecastHubValidations")
)
```

## Context

This project is part of a larger effort to provide tools to create and run
a forecast hub. Please also refer to our other packages:

- [ForecastHubSubmissionApp](https://github.com/epiforecasts/ForecastHubSubmissionApp)
